\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    \usepackage[colorlinks=true,urlcolor=blue]{hyperref}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape \textbf{Amit Kumar Singh}}\\
	thegigasurgeon@gmail.com $\cdot$ +91-9915503368 $\cdot$ \href{https://gigasurgeon.github.io/portfolio/}{gigasurgeon.github.io/portfolio} $\cdot$ \href{https://www.linkedin.com/in/thegigasurgeon/}{www.linkedin.com/in/thegigasurgeon}\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}
\textbf{Real Brokerage} \hfill Delhi, India\\
\textit{AI ML Engineer} \hfill Oct 2024 - Present\\
\begin{itemize} \itemsep 1pt
  \item Pretrained and Finetuned of state-of-the-art LLMs and VLMs with reasoning and thinking capabilities, including \textbf{LLaMA 3.3, Qwen 2.5 72B, Qwen 3, Gemma}, using \textbf{LoRA/QLoRA and GRPO-based RL post-training}, tailored for real estate auto-review.
  \item Currently leading development of enterprise-scale agentic AI document intelligence platform processing \textbf{80K+ PDFs daily}, leveraging \textbf{multi-agent text+visual reasoning pipelines} including\textbf{ tool-calling, subagents, skills.}
  \item Built a scalable \textbf{Multi-LLM Orchestration} Infrastructure to facilitate a lot of automation within the organization saving \textbf{1000s }of developer hours every week.
  \item Finetuned \textbf{Google Gemini-3.5-Pro, Gemini-3.5-Flash, GPT 4o} for robust multi-llm agentic workflow.
  \item End-to-End precise RAG pipeline using \textbf{intent routing,} \textbf{semantic chunking}, \textbf{llm reasoning},  \textbf{hybrid vector retrieval}, \textbf{context optimization}, \textbf{multi-source context aggregation},  embedding generation and structured output generation.
  \item \textbf{Claude Agent SDK} integration for automated PR reviews, incident investigation, and webhook-driven workflows
  \item Led an 8-person developer's team coordinating validator development across jurisdictions.
  \item   Built high-precision information extraction pipelines for unstructured real estate documents using \textbf{YOLOv9, Doctr OCR, and custom VLMs}, boosting accuracy from \textbf{35\% to 99.85\%}.
  \item Engineered scalable ML pipelines fusing \textbf{5+ specialized models} (VLMs, LLMs, OCR, Object Detection, embeddings) in a single application, deployed as \textbf{microservices on Kubernetes} across AWS and GCP, processing \textbf{80k} \textbf{PDFs} per day.
  \item Achieved a \textbf{200\%} pipeline speedup through graph optimizations, batched inference, model quantization (\textbf{INT8/FP16, AWQ/GPTQ}), and architecture-level modifications for fast inference.

\end{itemize}

\textbf{Streamingo AI} \hfill Noida, India\\
\textit{Deep Learning Engineer} \hfill Nov 2022 -- Oct 2024
\begin{itemize} \itemsep 1pt
  \item Developed end-to-end temporal event understanding systems using \textbf{Swin, VideoMAE, MVD, ViT, BEiT}.
  \item Worked on problems like video activity recognition, player tracking, pose detection, basketball court localization, face blurring, logo identification, zero shot classification, planogram compliance, etc. on videos and images.
  \item Designed zero-shot and few-shot classification systems using \textbf{CLIP, Detic, Prototypical Networks}, enabling rapid scalability across unseen classes.
  \item Built a real-time sports analytics engine combining object detection, multi-object tracking, pose estimation, and court localization.
  \item Deployed optimized inference pipelines using \textbf{TensorRT} and {ONNX}, delivering \textbf{3x} FPS.
\end{itemize}

\textbf{Attentive AI} \hfill Noida, India\\
\textit{Computer Vision Research Engineer} \hfill Apr 2021 -- Nov 2022
\begin{itemize} \itemsep 1pt
	\item Built and trained State Of The Art neural networks for image segmentation in satellite imagery i.e.\textbf{ HRNet, Vision Transformer}.
	\item End to end ownership of CV products (Falcon and Respod) across the company.
	\item Improved accuracy of models by 12\% and reduced overall post-processing time by 90\%.
\end{itemize}

\textbf{Nokia} \hfill Bangalore, India\\
\textit{Software Engineer} \hfill Jul 2020 -- Mar 2021
\begin{itemize} \itemsep 1pt
  \item Created a meta-learning platform for dynamic model selection and hyperparameter optimization across various business problems.
  \item Integrated Explainable AI (XAI) modules using SHAP, LIME for model interpretability and compliance.
\end{itemize}

\vspace{2mm}
%==== Projects ====%%
\header{Projects}

\textbf{Basketball Video to 3D Mapping} \textit{(PyTorch, Visual SLAM, ORBv3, Blender, Homography, VideoMAE)}\\
Reconstructed player trajectories in 3D from monocular sports footage using deep video transformers and traditional SLAM pipelines. Added temporal event summarization via transformer-based description generation.

\vspace{1mm}
\textbf{Tekken with Pose} \textit{(YOLOvNAS, Pose Estimation, Raspberry Pi)}\\
Created a camera-driven interface to map real-world actions into virtual gameplay using pose estimation, latency-aware gesture recognition, and control mapping.

\vspace{2mm}
\textbf{Charlie - AI Virtual Assistant} \textit{(Raspberry Pi, Python, STT, FaceNet)}\\
Built an edge-deployable assistant with multi-modal recognition: speaker ID, facial login, offline STT, and contextual response generation.\\
\vspace{2mm}
%==== Skills ====%%
\header{Skills}
\begin{tabular}{ l p{5.1in} }
  Programming Languages: & Python, C++, JavaScript \\
  ML / Post-Training: & GRPO (RL), LoRA/QLoRA, distillation, quantization (INT8/FP16, AWQ/GPTQ), agentic AI (tool-calling, subagents), RAG, multimodal fine-tuning \\
  Libraries \& Infra: & PyTorch, TensorFlow, Langchain, Claude Agent SDK, Detectron2, OpenCV, TensorRT, ONNX, Kubernetes, Docker, microservices, AWS, GCP
\end{tabular}

%==== Education ====%%
\vspace{2mm}
\header{Education}
\textbf{Chandigarh University} \hfill B.Tech. in Computer Science\\
\textit{GPA: 8.28}\

\end{document}
